%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{article} % Document font size and paper size


\usepackage{fontspec} % Allows the use of OpenType fonts
%\usepackage{libertine}
\usepackage{geometry} % Allows the configuration of document margins
\geometry{a4paper, textwidth=5.75in, textheight=9.5in, marginparsep=7pt, marginparwidth=.5in} % Document margin settings
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\footnotesize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar
\definecolor{myblue}{RGB}{0, 158, 184}
\definecolor{dartmouthgreen}{RGB}{0, 105, 62}
%\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={Jeremy
%R. Manning's CV},pdfauthor={Jeremy R. Manning}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Jeremy
R. Manning's CV},pdfauthor={Jeremy R. Manning}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
% Link colors
%\hypersetup{linkcolor=myblue,citecolor=black,filecolor=black,urlcolor=myblue}
\usepackage{etaremune}
\usepackage{soul}
\usepackage{multicol}

\hypersetup{linkcolor=dartmouthgreen,citecolor=black,filecolor=black,urlcolor=dartmouthgreen} % Link colors

% %----------------------------------------------------------------------------------------
% %	FONT CONFIGURATIONS
% %----------------------------------------------------------------------------------------

% % Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% % To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine} % Main text font
\setromanfont{Dartmouth Ruzicka}
\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\large} % Set font options for subsections
\subsubsectionfont{\mdseries\normalsize} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% % Hoefler Text Font (bundled with Mac OSX)
% \setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
% \setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
% \setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
% \newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
% \sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
% \subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
% \subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

% ----------------------------------------------------------------------------------------

% footnotes without numbers
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Jeremy R. Manning, \textsc{Ph.D.}}\\ % Your name
Director, Contextual Dynamics Laboratory\\[0.25cm]
Department of Psychological and Brain Sciences\\
Dartmouth College\\ % Your address
\textsc{HB} 6207, Moore Hall\\
Hanover, \textsc{NH}  03755\\
\textsc{U.S.A.}\\[.2cm]
\textsc{Email}: \href{mailto:jeremy.r.manning@dartmouth.edu}{jeremy.r.manning@dartmouth.edu}\\
% Your email address
\textsc{Phone}: \href{tel:6036462777}{603.646.2777}\\ % telephone number
\textsc{URL}:
\href{http://www.context-lab.com}{http://www.context-lab.com}\\ % academic/personal website

\section*{Employment}
\emph{Associate Professor},
\textbf{Dartmouth College}, Hanover, NH (2024 -- )\\
Department of Psychological and Brain Sciences \\
Additional affiliation: Cognitive Science\\
Tenured: 2024\\[.1cm]

\emph{Assistant Professor},
\textbf{Dartmouth College}, Hanover, NH (2015 -- 2024)\\
Department of Psychological and Brain Sciences \\
Additional affiliation: Cognitive Science\\
Reappointed: 2018\\[.1cm]

\emph{Postdoctoral Research
  Associate}, \textbf{Princeton University}, Princeton, NJ (2011 -- 2015)\\
Princeton Neuroscience
Institute and Department of Computer Science\\
Advisors: Kenneth Norman, \textsc{Ph.D.} and David Blei, \textsc{Ph.D.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section*{Education}

\textsc{Ph.D.} in Neuroscience, \textbf{University of Pennsylvania},
Philadelphia, PA (2011)\\
Advisor:  Michael Kahana, \textsc{Ph.D.}\\
Dissertation: \textit{Acquisition, storage, and
    retrieval in digital and biological brains}\\[.1cm]

\textsc{B.S.} in Neuroscience (High honors, \textit{Magna cum laude}), {\bf Brandeis University},
Waltham, MA (2006)\\
Advisor: Robert Sekuler, \textsc{Ph.D.}\\
Dissertation: \textit{Modeling human spatial navigation using a
    degraded ideal navigator}\\[0.05cm]

\textsc{B.S.} in Computer Science (\textit{Magna cum
  laude}), {\bf Brandeis University},
Waltham, MA (2006)

%----------------------------------------------------------------------------------------
%	GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\section*{Grants, honors, and awards (selected)}
\begin{etaremune}
\item Linda B. and Kendrick R. Wilson III 1969 Fellowship (2024--2025)
\item John M. Manley Huntington Award for Newly Tenured Faculty (2024)\\
  Awarded to recently tenured Dartmouth faculty members who have an outstanding record of teaching and research
\item CompX Faculty Grant (2024): Developing the next generation of multi-scale large language
  models\\
  Award amount: \$15,000; Role: PI
\item NSF CAREER Award (2022): Mapping and enhancing the acquisition
of conceptual knowledge using behavior, neural signals, and natural
language processing models\\
Award amount: \$881,612; Role: PI
\item Elected member, Memory Disorders Research Society (2021)
\item NIMH Grant (2021): Serotonin modulation of the development of
neural circuits underlying reward processing and impulsivity in
adolescents\\
Award amount: \$568,974; Role: Co-I (PI: Katherine Nautiyal)
\item NIH Grant Supplement (2019): Dissecting serotonergic and
dopaminergic contributions to the neural circuits underlying impulsive
behavior\\
Award amount: \$93,190; Role: Co-I (PI: Katherine Nautiyal)
\item National Institute on Drug Abuse Center for Technology and Behavioral Health Pilot Grant (2019): Linking
mental health and exercise via remote sensing\\
Award amount: \$20,000; Role: Co-PI (PI: David Bucci; Co-PI: Lorie
Loeb)
\item Dartmouth Junior Faculty Fellowship (2018)
\item Walter and Constance Burke Research Initiation Award (2018)\\
Award amount: \$25,000; Role: PI
\item DARPA Grant: Memory Enhancement with Modeling (MEM; 2018)\\
Award amount: \$55,558; Role: PI (sub-award of DARPA RAM
N66001-14-2-4-032)
\item i-CORPS Pilot Grant: Developing a mobile device for estimating
dynamic attention states (2018).\\Award amount: \$3,000; Role: Co-PI (PI: Peter Tse)
\item Diamond Research Development Award (2017): Improving memory and context reinstatement at perceptual event boundaries\\
Award amount: \$199,997; Role: Co-PI (PI: Barbara Jobst)
\item Dartmouth Leslie Center for the Humanities award for developing a
course incorporating the theme of ``revolution'' (2017; for
\textit{Storytelling with Data; PSYC 81.06}).\\Award amount: \$5,000;
Role: Course Instructor
\item Social Impact Practicum (2017; for \textit{Storytelling with Data; PSYC
  81.06})\\Award amount: \$2,000; Role: Course Instructor
\item Young Minds and Brains (2017): The impact of exercise on attention, memory,
and stress\\
Award amount: \$100,000; Role: PI (with David Bucci, Co-PI)
\item NSF EPSCoR Grant (2016): The neural basis of attention\\Award
amount: \$6,000,000; Role: Co-I (PI: Peter Tse)
\item NIMH Ruth L. Kirshstein National Research Service Award for an
  Individual Predoctoral Fellowship (2010): The neural representation of
  context and its role in free recall\\Award amount: \$57,762; Role:
  PI
\item NIH Computational Neuroscience Training Grant (2008)\\
Role: Trainee
\item NIH Systems and Integrative Biology Training
Grant (2006)\\Role: Trainee
\end{etaremune}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%-------------------------------------------------------------------------------------------

\section*{Publications}\blfootnote{Undergraduate trainees are denoted by
  \ul{underlined} text, graduate trainees are indicated by \textit{italicized} text, and postdoctoral trainees are indicated by \ul{\textit{underlined and italicized}} text.}

\vspace{-0.4in}
\begin{etaremune}
\item \textit{Fitzpatrick PC}, \ul{\textit{Heusser AC}}, \textbf{Manning JR} (2025) Text embedding models yield
high-resolution insights into conceptual knowledge from short multiple-choice
quizzes. \textit{Nature Communications}: In press.

\item \ul{Stropkay HF}, Chen J, Latifi MJ, Rockmore DN, \textbf{Manning JR} (2025)) A stylometric application of large language models. \textit{arXiv}: 2510.21958.

\item \textbf{Manning JR} (2025) Why we're so preoccupied by the past.  \textit{Scientific American}, online.

\item \textit{Owen LLW}, \textbf{Manning JR} (2024) High-level cognition is supported by
information-rich but compressible brain activity
patterns. \textit{Proceedings of the National Academy of Sciences, USA}, 121(35): e2400082121.

\item \textit{Xu X}, Zhu Z, Zheng X, \textbf{Manning JR} (2024) Temporal
asymmetries in inferring unobserved past and future events. \textit{Nature
Communications}, 15: 8502.

\item \ul{\textit{Jolly E}}, \textit{Sadhukha S}, \ul{Iqbal M}, \ul{Molani Z}, \ul{Walsh T}, \textbf{Manning JR},
  Chang LJ (2023) People are represented and remembered through their
  relationships with others. \textit{PsyArXiv}: bw9r2.

\item \textit{Ziman K}, \ul{Lee MR}, \ul{Martinez AR}, \textbf{Manning JR} (2023) Category-based
and location-based volitional covert attention are mediated by
different mechanisms and affect memory at different timescales.
\textit{PsyArXiv}: 2ps6e. 

\item \textbf{Manning JR}, Whitaker EC, \ul{Fitzpatrick PC}, \ul{Lee MR}, \ul{Frantz AM},
\ul{Bollinger BJ}, \ul{Ro\-man\-o\-va D}, \ul{Field CE}, \ul{\textit{Heusser AC}} (2023) Feature and order
manipulations in a free recall task affect memory for current and future lists.
\textit{PsyArXiv}: erzfp.  (Under second round of reviews at Psychological Review)

\item \textit{Fitzpatrick PC}, \textbf{Manning JR} (2023)
\texttt{davos}: a Python package ``smuggler'' for con\-struct\-ing
light\-weight reproducible notebooks.  \textit{SoftwareX}: in press.

\item  \textbf{Manning JR} (2023) Context reinstatement. In Kahana MJ and
Wagner AD, Ed. \textit{Handbook of Human Memory}. New York, NY:
Oxford University Press. Chapter 38.

\item \textbf{Manning JR} (2023) Identifying
stimulus-driven neural activity patterns in multi-pa\-tient intracranial recordings.
In Axmacher N, Ed. \textit{Intracranial EEG for Cognitive
  Neuroscience}.  New York, NY: Springer. Chapter 48.

\item \textbf{Manning JR}, \ul{\textit{Notaro GM}}, \ul{Chen E}, \ul{Fitzpatrick PC}
(2022) Fitness tracking reveals task-specific associations between
memory, mental health, and physical activity.  \textit{Scientific
  Reports}, 12: 13822.

\item Kumar M, Anderson MJ, Antony  JW, Baldassano C, Brooks PP, Cai MB,
Chen P-HC, Ellis CT, Hens\-el\-man-Petrusek G, Huberdeau D, Hutchinson BJ,
Li PY, Lu Q, \textbf{Manning JR}, Mennen AC, Nastase SA, Richard H,
Schapiro AC, Schuck NW, Suo D, Turek JS, Vo VA, Wallace G, Wang Y,
Zhang H, Zhu X, Capotă M, Cohen JD, Hasson U, Li K, Ramadge PJ,
Turk-Browne NB, Willke TL, Norman KA (2022) BrainIAK: the brain
imaging analysis kit.  \textit{Aperture}, 1(4): 1--19.

\item Scangos KW, Khambhati AN, Daly PM, \textit{Owen LLW},
\textbf{Manning JR}, Ambrose JB, Austin E, Dawes HE, Krystal AD, Chang
EG (2021) Distributed subnetworks of depression defined by direct
intracranial neurophysiology.  \textit{Frontiers in Human
  Neuroscience}, 15: doi.\-org/\-10.\-3389/\-fnhum.\-2021.\-746499. 

\item \textit{Chen HT}, \textbf{Manning JR}, van der Meer MAA (2021)
Between-subject prediction reveals a shared representational geometry
in the rodent hippocampus.  \textit{Current Biology}, 31:
1--12. 

\item \textit{Owen LLW}, \textit{Chang TH}, \textbf{Manning JR} (2021) High-level
cognition during story listening is reflected in high-order dynamic
correlations in neural activity patterns.  \textit{Nature
  Communications}, 12(5728): doi.\-org/\-10.1038/\-s41467-021-25876-x. 

\item \textbf{Manning JR} (2021) Episodic memory: mental time travel or a
quantum `memory wave' function? \textit{Psychological Review}, 128(4):
711--725. 

\item Chang LJ, \ul{\textit{Jolly E}}, \textit{Cheong JH},
\textit{Rapuano K}, \ul{Greenstein N}, \ul{\textit{Chen PHA}}, \textbf{Manning JR} (2021)
Endogenous variation in ventromedial prefrontal cortex state dynamics
during naturalistic viewing reflects affective
experience. \textit{Science Advances}, 7(17): eabf7129. 

\item  \textit{Xie T}, \textit{Cheong JH}, \textbf{Manning JR}, Brandt AM, Aronson
JP, Jobst BC, Bujarski KA, Chang LJ (2021) Minimal functional
alignment of ventromedial prefrontal cortex intracranial EEG signals
during naturalistic viewing.  \textit{bioRxiv}: 443308. 

\item \textit{Ziman K}, \textbf{Manning JR} (2021) Unexpected false feelings of
familiarity about faces are associated with increased pupil
dilations.  \textit{bioRxiv}: 432360. 

\item \ul{\textit{Heusser AC}}, \ul{Fitzpatrick PC}, \textbf{Manning JR} (2021) Geometric models reveal
behavioral and neural signatures of transforming naturalistic experiences into
episodic memories. \textit{Nature Human Behaviour}:
doi.org/\-10.1038/\-s41562-\-021-\-01051. 

\item \textit{Owen LLW}, \ul{Muntianu TA}, \ul{\textit{Heusser AC}}, Daly P, Scangos K,
\textbf{Manning JR} (2020) A Gaussian process model of human
electrocorticographic data. {\em Cerebral Cortex}, 30(10):
5333--5345. 

\item  Chang L, \textbf{Manning JR}, Baldassano C, de la Vega A, Fleetwood G,
Geerligs L, Haxby J, Lahnakoski J, Parkinson C, Shappell H, Shim WM,
Wager T, Yarkoni T, Yeshurun Y, Finn E (2020) Naturalistic data
analysis: doi.org/\-10.5281/\-zen\-o\-do.\-3937849.

\item  \ul{\textit{Heusser AC}}, \textit{Ziman K}, \textit{Owen LLW}, \textbf{Manning JR} (2018)
HyperTools: a Python toolbox for gaining geometric insights into
high-dimensional data. {\em Journal of Machine Learning Research}, 18:
1--6. 

\item \textit{Ziman K}, \ul{\textit{Heusser AC}}, \ul{Fitzpatrick PC}, \ul{Field CE}, \textbf{Manning JR} (2018) Is
automatic speech-to-text transcription ready for use in psychological
experiments? {\em Be\-hav\-ior Re\-search Meth\-ods}:
doi.\-org/\-10.3758/s13428-018-1037-4. 

\item \ul{\textit{Heusser AC}}, \textbf{Manning JR} (2018) Capturing the geometric structure
of episodic memories for naturalistic experiences. \textit{Conference on
Cognitive Computational Neuroscience}:
doi.\-org/\-10.\-32470/\-CCN.\-2018.\-1267-0.

\item \textbf{Manning JR}, Zhu X, Willke TL, \textit{Ranganath R}, \textit{Stachenfeld K}, Hassan U,
Blei DM, Norman KA (2018) A probabilistic approach to discovering dynamic
full-brain functional connectivity patterns. {\em NeuroImage}, 180:
243--252. 

\item  \ul{\textit{Heusser AC}}, \ul{Fitzpatrick PC}, \ul{Field CE}, \textit{Ziman K}, \textbf{Manning JR}
(2017) Quail: a Python toolbox for analyzing and plotting free recall data.
{\em The Journal of Open Source Software}, 2(18): 424. 

\item  \textbf{Manning JR}, Hulbert JC, Williams J, \textit{Piloto L}, Sahakyan L,
Norman KA (2016) A neural signature of contextually mediated intentional
forgetting. {\em Psychonomic Bulletin and Review}, 23(5): 1534--1542. 

\item Anderson MJ, Capota M, Turek JS, Zhu X, Willke TL, Wang Y, \textit{Chen P-H},
\textbf{Manning JR}, Ramadge PJ, Norman KA (2016) Enabling factor analysis on
thousand-subject neuroimaging datasets. \textit{IEEE Xplore, International
Conference on Big Data (BigData 2016)}:
doi.\-org/\-10.1109/\-BigData.\-2016.\-7840719.

\item  Benson NC, \textbf{Manning JR}, Brainard DH (2014) Unsupervised
learning of cone spectral classes from natural images. {\em PLoS Computational
Biology}, 10(6): e1003652. 

\item \textbf{Manning JR}, Ranganath R, Norman KA, Blei DM (2014) Topographic factor
analysis: a Bayesian model for inferring brain networks from neural data. {\em
PLoS One}, 9(5): e94914. 

\item \textbf{Manning JR}, Lew TF, Li N, Ka\-ha\-na MJ, Se\-ku\-ler RW (2014)
MA\-GELL\-AN: a cog\-ni\-tive map-based mo\-del of hu\-man way\-find\-ing. {\em
Journal of Experimental Psychology: General}, 143(3): 1314--1330.  

\item  \textbf{Manning JR}, Ranganath R, Keung W, Turk-Browne N, Cohen
JD, Norman KA, Blei DM (2014) Hierarchical Topographic Factor Analysis.
\textit{IEEE Xplore, 4\textsuperscript{th} International Workshop on Pattern
Recognition in Neuroimaging}: doi.\-org/\-10.1109/\-PRNI.\-2014.\-6858530.

\item  \textbf{Manning JR}, Kahana MJ, Norman KA (2014) The role of
context in memory. In Gazzaniga M, Ed. \textit{The Cognitive Neurosciences,
Fifth Edition}. Cambridge, MA: MIT Press. Chapter 47.

\item  \textbf{Manning JR}, Kahana MJ (2012) Interpreting semantic
clustering effects in free recall. \textit{Memory}, 20(5): 511--517.  

\item \textbf{Manning JR}, Sperling MR, Sharan A, Rosenberg EA, Kahana MJ (2012)
Spontaneously reactivated patterns in frontal and temporal lobe predict
semantic clustering during memory search. \textit{The Journal of Neuroscience},
32(26): 8800--8816.  

\item  \textbf{Manning JR}, Gershman SJ, Norman KA, Blei DM (2012) Factor
topographic latent source analysis: factor analysis for brain images.
\textit{Neural Information Processing Systems (NeurIPS) Workshop on Machine
Learning and Interpretation in Neuroimaging}, 2: Online.

\item  \textbf{Manning JR}, Polyn SM, Baltuch G, Litt B, Kahana MJ (2011)
Oscillatory patterns in temporal lobe reveal context reinstatement during
memory search. \textit{Proceedings of the National Academy of Sciences of the
United States of America}, 108(31): 12893--12897.  

\item  Jacobs J, \textbf{Manning JR}, Kahana MJ (2010) Response to
Miller: ``broadband'' vs. ``high gamma'' electrocorticographic signals.
\textit{The Journal of Neuroscience}, 30(19): Online.  

\item  \textbf{Manning JR}, Jacobs J, Fried I, Kahana MJ (2009) Broadband
shifts in local field potential power spectra are correlated with single-neuron
spiking in humans. \textit{The Journal of Neuroscience}, 29(43): 13613--13620.
 

\item \textbf{Manning JR}, Brainard DH (2009) Optimal design of photoreceptor
mosaics: why we do not see color at night. \textit{Visual Neuroscience}, 26:
5--19.

% Kumar M, Anderson MJ, Antony JW, Baldassano C, Brooks PP, Cai MB, Chen P-HC,
% Ellis CT, Hens\-el\-man-Petrusek G, Huberdeau D, Hutchinson BJ, Li PY, Lu Q,
% \textbf{Manning JR}, Mennen AC, Nastase SA, Richard H, Schapiro AC, Schuck NW,
% Suo D, Turek JS, Vo VA, Wallace G, Wang Y, Zhang H, Zhu X, Capotă M, Cohen JD,
% Hasson U, Li K, Ramadge PJ, Turk-Browne NB, Willke TL, Norman KA (2020)
% BrainIAK: The Brain Imaging Analysis Kit. \textit{OSF Preprints}:
% 10.31219/osf.io/db2ev. \textbf{Now in press at {\em Aperture}}\\[0.05cm]

% Heusser AC, Fitzpatrick PC, \textbf{Manning JR} (2020) % Geometric models
% reveal behavioral and neural signatures of transforming naturalistic
% experiences into episodic memories. \textit{bioRxiv}: 409987. \textbf{Now
% published in {\em Nature Human Behaviour}}\\[0.05cm]

% Scangos KW, Khambhati AN, Daly PM, Owen LW, \textbf{Manning JR},
% Ambrose JB, Austin E, Dawes HE, Krystal AD, Chang EG (2020) Biomarkers
% of depression symptoms defined by direct intractranial
% neurophysiology.  \textit{bioRxiv}: 943118 \textbf{Now in press at
%   {\em Frontiers in Human Neuroscience}}\\[0.05cm]

% HT Chen, \textbf{JR Manning}, MAA van der Meer (2020)
% Between-subject prediction reveals a shared representational geometry
% in the rodent hippocampus.  \textit{bioRxiv}: 92206. \textbf{Now
%   published in {\em Current Biology}}\\[0.05cm]

% \years{2019} Owen LLW, Chang TH, \textbf{Manning JR} (2019) High-level
% cognition during story listening is reflected in high-order dynamic
% correlations in neural activity patterns.  \textit{bioRxiv}:
% 763821. \textbf{Now in press at {\em Nature Communications}}\\[0.05cm]

% \textbf{Manning JR} (2019) Episodic memory: mental time travel or a
% quantum `memory wave' function? \textit{PsyArXiv}: 6zjwb. \textbf{Now
%   published in {\em Psychological Review}}\\[0.05cm]

% \years{2018} Chang LJ, Jolly E, Cheong JH,
% Rapuano K, Greenstein N, Chen PHA, \textbf{Manning JR} (2018)
% Endogenous variation in ventromedial prefrontal cortex state dynamics
% during naturalistic viewing reflects affective experience.
% \textit{bioRxiv}: 487892.  \textbf{Now published in {\em Science Advances}}\\[0.05cm]

% Owen LLW, Heusser AC, \textbf{Manning JR} (2018) A Gaussian process model of
% human electrocorticographic data. \textit{bioRxiv}: 121020.  \textbf{Now published in {\em Cerebral Cortex}}\\[0.05cm]

% \years{2017} Ziman K, Heusser AC, Fitzpatrick PC, Field CE,
% \textbf{Manning JR} (2017) Is automatic speech-to-text transcription
% ready for use in psychological experiments?  \textit{PsyArXiv}:
% psh48. \textbf{Now published in {\em Behavior Research Methods}}\\[0.05cm]

% \textbf{Manning JR}, Zhu X, Willke TL, Ranganath R, Stachenfeld KL,
% Hasson U, Blei DM, Norman KA (2017) A probabilistic approach to
% discovering dynamic full-brain functional connectivity
% patterns.  \textit{bioRxiv}: 106690. \textbf{Now published in {\em NeuroImage}}\\[0.05cm]

% Heusser AC, Ziman K, Owen LLW, \textbf{Manning JR} (2017) HyperTools: a
% Python toolbox for visualizing and manipulating high-dimensional
% data. \textit{arXiv}: 1701.08290. \textbf{Now published in {\em Journal
%   of Machine Learning Research}}\\[0.05cm]

% \years{2016} Anderson MJ, Capota M, Turek JS, Zhu X, Willke TL, Chen
% P-H, \textbf{Manning JR}, Ramadge PJ, Norman KA (2016)  Enabling Factor
% Analysis on Thousand-Subject Neuroimaging Datasets.  \textit{arXiv}:
% 608.04647. \textbf{Now published in {\em IEEE Xplore}}

%\subsection*{Book chapters}
\end{etaremune}


\section*{Invited talks (selected)}

\begin{multicols}{2}
\begin{etaremune}
\item Generative Episodic Memory: Constructing Scenarios of the Past (Keynote Speaker, 2025)
\item Brandeis University (2025)
\item University of Virginia (2024)
\item University of Pennsylvania (2023)
\item Cornell University (2023)
\item Boston University (2023)
\item Harvard University (2022)
\item University of California, Irvine (2022)
\item Ruhr Universit\"{a}t Bochum (2022)
\item Microsoft Research (2022)
\item Carnegie Mellon University (2021)
\item National Institutes of Mental Health (2021)
\item Boston College (2020)
\item Facebook Reality Labs (2020)
\item University of California, Berkeley (2020)
\item University of Oregon (2020)
\item Context and Episodic Memory Symposium (2019)
\item Society for Affective Science (2019)
\item Uber (2019)
\item Northeastern University (2018)
\item Society for Neuroscience (2018)
\item University of Pennsylvania (2018)
\item Bard College (2017)
\item Harvard University (2017)
\item University of Texas at Austin (2017)
\item Society for Neuroscience (2016)
\item Brown University (2015)
\item Columbia University (2015)
\item Dartmouth College (2015)
\item Georgetown University (2015)
\item Johns Hopkins University (2015)
\item Context and Ep\-is\-od\-ic Mem\-o\-ry Symposium (2014)
\item Manhattan Area Memory Meeting (2014)
\item Pattern Recognition in Neuroimaging (2014)
\item Context and Episodic Memory Symposium (2013)
\item University of Massachusetts, Amherst (2013)
\item Dartmouth College (2013)
\item Charles River Analytics (2012)
\item Natick Soldier Systems Center (2012)
\item Princeton University (2011)
\item Society for Mathematical Psychology (2011)
\item University of Pennsylvania (2011)
\end{etaremune}
\end{multicols}
  
\section*{Software (selected)}

\begin{etaremune}
\item \textbf{Manning JR}, \textit{Manjunatha H}, Kording K (2023) Chatify: add an LLM-based chatbot ``tutor'' to
Jupyter notebooks. \href{https://github.com/ContextLab/chatify}{GitHub}.
\item \textit{Fitzpatrick PC}, \textbf{Manning JR} (2022) Davos: import
Python packages, even if they aren't installed.  \href{https://github.com/ContextLab/davos}{GitHub}. 
\item \textbf{Manning JR} (2021) DataWrangler: format and clean
data, with a special focus on applying natural language processing
models to text data.  \href{https://github.com/ContextLab/data-wrangler}{GitHub}. 
\item \textit{Owen LLW}, \textit{Chang TH}, \textbf{Manning JR} (2019) Timecorr
Toolbox: compute high-order correlations in multivariate timeseries
data.  \href{https://github.com/ContextLab/timecorr}{GitHub}. 
\item \textit{Owen LLW}, \ul{\textit{Heusser AC}}, \textbf{Manning JR} (2018) SuperEEG Toolbox:
infer full-brain activity patterns from a small(ish) number of ECoG electrodes using Gaussian process regression. \href{https://github.com/ContextLab/superEEG}{GitHub}. 
\item Capota M, Turek J, \textit{Chen P-HC}, Zhu X, \textbf{Manning JR}, Sundaram N,
Keller B, Wang Y, Shin YS (2017) BrainIAK: Brain Imaging Analysis Kit. \href{http://brainiak.org/}{brainiak.org}.
\item \ul{\textit{Heusser AC}}, \textit{Ziman K}, \ul{Fitzpatrick PC}, \ul{Field CE}, \textbf{Manning JR}
(2017) AutoFR: a scalable verbal free recall experiment with
automatic speech-to-text transcription.
\href{https://github.com/ContextLab/autoFR}{GitHub}. 
\item \ul{\textit{Heusser AC}}, \ul{Fitzpatrick PC}, \ul{Field CE}, \textit{Ziman K}, \textbf{Manning JR}
(2017) Quail: a Python toolbox for analyzing and plotting free recall
data. \href{https://github.com/ContextLab/quail}{GitHub}. 
\item \ul{\textit{Heusser AC}}, \textit{Ziman K}, \textit{Owen LLW}, \textbf{Manning JR} (2017)
HyperTools: gain geometric insights into high-dimensional data (Python).  \href{https://github.com/ContextLab/hypertools}{GitHub}. 
\item \textbf{Manning JR} (2016) Hyperplot Tools: gain
geometric insights into high-dimensional data (MATLAB).
  \href{http://www.mathworks.com/matlabcentral/fileexchange/56623}{MATLAB
  Central File Exchange: 56623}.  
\item \textbf{Manning JR} (2014) Hierarchical Topographic
Factor Analysis: 
  \href{https://app.box.com/s/elcxpst2n0q6elpuzndj}{efficiently identify func\-tion\-al brain networks in fMRI data}.
\item \textbf{Manning JR} (2013)  MATLAB Ipsum: generate filler text using MATLAB.  \href{http://www.mathworks.com/matlabcentral/fileexchange/43428}{MATLAB
  Central File Exchange: 43428}.  
\item \textbf{Manning JR} (2013)  Easy resample: simple interface for
  interpolating or resampling a 1\textsc{d} signal.  \href{http://www.mathworks.com/matlabcentral/fileexchange/43320}{MATLAB
  Central File Exchange: 43320}.  
\item \textbf{Manning JR} (2012)  Chuck Close-ify: automatically create
  artwork in Chuck Close's iconic style based on existing photographs.  \href{http://www.mathworks.com/matlabcentral/fileexchange/38770}{MATLAB
  Central File Exchange: 38770}.  
\item \textbf{Manning JR} (2012)  Plot fMRI images: quick and easy method
    for generating 2\textsc{d} and 3\textsc{d} brain plots.  \href{http://www.mathworks.com/matlabcentral/fileexchange/36139}{MATLAB Central File
    Exchange: 36139}.  
\item \textbf{Manning JR} (2012)  Generate synthetic fMRI data: generate
    synthetic data for testing fMRI analyses and models.  \href{http://www.mathworks.com/matlabcentral/fileexchange/36125}{MATLAB Central File
    Exchange: 36125}.  
\item \textbf{Manning JR} (2012)  Sane pColor: create 2\textsc{d} images that
    don't look blurry in OS X's Preview PDF viewer.  \href{http://www.mathworks.com/matlabcentral/fileexchange/35601}{MATLAB Central File
    Exchange: 35601}.  
\item \textbf{Manning JR} (2012)  Attach: MATLAB implementation of the attach
    function in R.  \href{http://www.mathworks.com/matlabcentral/fileexchange/35436}{MATLAB Central File
    Exchange: 35436}.  
\item \textbf{Manning JR} (2012)  Get tight subplot handles: allows user to
    exert finer control over subplot spacing in MATLAB.  \href{http://www.mathworks.com/matlabcentral/fileexchange/35435}{MATLAB Central File
    Exchange: 35435}.  
\item \textbf{Manning JR} (2012)  Slices: efficiently slice a tensor
    along the $n^\mathrm{th}$ dimension. \href{http://www.mathworks.com/matlabcentral/fileexchange/35439}{MATLAB Central File
    Exchange: 35439}.
\end{etaremune}


\section*{Teaching and instruction}

  \subsection*{Open courses (selected)}

  \begin{etaremune}
\item \href{https://github.com/ContextLab/experimental-psychology}{Laboratory in Psychological Science};  doi.org/10.5281/zenodo.6596761
\item \href{https://github.com/ContextLab/human-memory}{Human
    Memory};  doi.org/10.5271/zenodo.5182787
\item  \href{https://github.com/ContextLab/cs-for-psych}{Introduction to
    Programming for Psychological Scientists};  doi.org/10.5281/zenodo.5136795
\item  \href{https://naturalistic-data.org/content/intro.html}{Naturalistic
    data analysis}; doi.org/10.5281/zenodo.3937849
\item  \href{https://github.com/ContextLab/storytelling-with-data}{Storytelling
    with Data};  doi.org/10.5281/zenodo.5182774
\item  \href{http://mindsummerschool.org/}{Methods in Neuroscience at Dartmouth Computational
    Summer School}
\item \href{https://github.com/ContextLab/computational-neuroscience}{Computational Neuroscience}; doi.org/10.5281/zenodo.10235877
  \end{etaremune}

  
% \subsection*{Dartmouth College}
% \years{2021} \textit{Instructor}, Human Memory (PSYC 51.09; \href{https://github.com/ContextLab/human-memory}{Website})\\
% \textit{Instructor}, Storytelling with Data (PSYC 81.09;
% \href{https://github.com/ContextLab/storytelling-with-data}{Website})\\
% \textit{Instructor}, Introduction to Programming for
% Psychological Scientists, Graduate level (PSYC 132;  \href{https://github.com/ContextLab/cs-for-psych}{Website}) \\[0.05cm]

% \years{2020} \textit{Co-organizer}, Neuroimaging Analysis Methods for
% Naturalistic Data (\href{http://naturalistic-data.org/intro}{Website}) \\[0.05cm]

% \textit{Instructor}, Introduction to Programming for
% Psychological Scientists, Undergraduate level (PSYC 32;  \href{https://github.com/ContextLab/cs-for-psych}{Website}) \\[0.05cm]

% \years{2019} \textit{Co-organizer}, Methods in Neuroscience at
% Dartmouth (MIND) computational
% summer school: cognitive maps
% (\href{http://mindsummerschool.org/}{Website}) \\[0.05cm]

% \years{2018} \textit{Co-organizer}, Methods in Neuroscience at
% Dartmouth (MIND) computational
% summer school: narratives and natural contexts
% (\href{http://mindsummerschool.org/}{Website}) \\[0.05cm]

% \years{2017}
% \textit{Instructor}, Storytelling with Data (PSYC 81.09; \href{https://github.com/ContextLab/storytelling-with-data}{Website})\\
% \textit{Instructor}, Laboratory in Psychological
% Science (PSYC 11)\\
% \textit{Instructor}, Human Memory (PSYC 51.09)\\
% \textit{Guest Lecturer}, Graduate Psychology Proseminar (PSYC
% 100.01)\\[0.05cm]
% \textit{Co-organizer}, Methods in Neuroscience at
% Dartmouth (MIND) computational
% summer school: multi-scale network dynamics (\href{http://mindsummerschool.org/}{Website}) \\[0.05cm]

\subsection*{Mentorship  (selected)}

%\subsubsection*{Dartmouth College}

\textit{Postdoctoral Advisees}:
\begin{etaremune}
\item Hung-Tu Chen (2024 -- 2025; current position: Meta)
\item Gina Notaro (2017 -- 2018; current position: HRL Laboratories)
\item Andrew Heusser (2016 -- 2018; current position: PyMC Labs)
\end{etaremune}

\textit{Graduate Advisees}:
\begin{etaremune}
\item Paxton Fitzpatrick (Doctoral student; 2021 -- )
\item Xinming Xu (Doctoral student; 2021 -- )
\item Mark Taylor (Masters student, Quantitative Biomedical Sciences; 2021)
\item Caroline Lee (Doctoral student; 2019 -- 2021)
\item Max Bluestone (Masters student, Quantitative Biomedical
Sciences; 2018 -- 2020)
\item Deepanshi Shokeen (Masters student, Quantitative Biomedical
Sciences; 2018 -- 2020)
\item Kirsten Ziman (Doctoral student; 2017 -- 2022; current position: Postdoctoral researcher at Princeton University)
\item Lucy Owen (Doctoral student; 2016 -- 2021; current position: Assistant Professor at University of Montana)
\item Tom Hao Chang (Masters student, Computer Science; co-advised with
Qiang Liu; 2016 -- 2017; current position: Robinhood)
\item Hanli Li (Masters student, Computer Science; co-advised with Qiang
Liu; 2016)
\end{etaremune}

\textit{Thesis Committees}:
\begin{etaremune}
\item Jane Han (Advisor: James Haxby)
\item Lindsey Tepfer (Advisor: Mark Thornton)
\item Arati Sharma (Advisor: Kate Nautiyal)
\item Clara Sava-Segal (Advisor: Emily Finn)
\item Manish Mohapatra (Advisor: Matthijs van der Meer; Graduated 2025)
\item Megan Hillis (Advisor: David Kraemer; Graduated 2025)
\item Omri Raccah (Advisor: David Poeppel; Graduated 2024)
\item Courtney Jiminez (Advisor: Meghan Meyer; Graduated 2024)
\item Hung-tu Chen (Advisor: Matthijs van der Meer; Graduated 2024)
\item Dhaval Bhatt (Advisor: Meghan Meyer; Graduated 2023)
\item Tiankang Xie (Advisor: Luke Chang; Graduated 2023)
\item Vassiki Chauhan (Advisors: Ida Gobbini and James Haxby; Graduated 2021)
\item Emily Irvine (Advisor: Matthijs van der Meer; Graduated 2020)
\item Eli Bowen (Advisor: Richard Granger; Graduated 2020)
\item Eshin Jolly (Advisor: Luke Chang; Graduated 2020)
\item Stephen Meisenhelter (Advisor: Barbara Jobst; Graduated 2020)
\item Feilong Ma (Advisor: James Haxby; Graduated 2019)
\item Kevin Hartstein (Advisor: Peter Tse; Graduated 2019)
\item Beau Sievers (Advisor: Thalia Wheatley; Graduated 2018)
\item Kristina Rapuano (Advisor: Luke Chang; Graduated 2018)
\item Luke Eglington (Advisor: Sean Kang; Graduated 2018)
\item Gina Notaro (Advisor: Solomon Diamond; Graduated 2017)
\end{etaremune}

\textit{Specialist Committees}:
\begin{etaremune}
\item Yuqi Zhang (Advisors: Richard Granger and James Haxby)
\item Covert Geary (Advisor: John Murray)
\item Menghan Yang (Advisor: Luke Chang)
\item Deepasri Prasad (Advisor: Caroline Robertson)
\item Zizhuang Miao (Advisor: Tor Wager)
\item Benjamin Graul (Advisor: Tor Wager)
\item Yeongji Lee (Advisor: David Kraemer)
\item Thomas Botch (Advisors: Emily Finn and Caroline Robertson)
\item Dhaval Bhatt (Advisor: Meghan Meyer)
\item Clara Sava-Segal (Advisor: Emily Finn)
\item Wasita Mahaphanit (Advisor: Luke Chang)
\item Jane Han (Advisor: James Haxby)
\item Megan Hillis (Advisor: Caroline Robertson)
\item Anna Mynick (Advisor: Caroline Robertson)
\item Marissa Clark (Advisor: Luke Chang)
\item Robert Quon (Advisor: Barbara Jobst)
\item Mira Nencheva (Advisor: Casey Lew-Williams)
\item Marvin Maechler (Advisor: Peter Tse)
\item Eli Bowen (Advisor: Richard Granger)
\item Emma Templeton (Advisor: Thalia Wheatley)
\item Feilong Ma (Advisor: James Haxby)
\item Youki Tanaka (Advisor: Matthijs van der Meer)
\end{etaremune}

\textit{Undergraduate Advisees}:
\blfootnote{Senior thesis students are denoted by asterisks
  (*)}
\begin{multicols}{2}
\begin{etaremune}
  \item Sam Haskel* (2025 -- )
  \item Harrison Stropkay* (co-advised with Daniel Rockmore; 2025)
  \item Kevin Chang (2025 -- )
  \item Andrew Richardson (2025 -- )
  \item Ben Hanson (2025 -- )
  \item Annabelle Morrow (2025 -- )
  \item Owen Phillips (2025 -- )
  \item Rodrigo Vega Ayllon (2025 -- )
  \item Joy Maina (2025 -- )
  \item Alexandra Wingo (2025 -- )
  \item Angelyn Liu (2025 -- )
  \item Miel Wewerka (2024 -- )
  \item Manraaj Singh (2024 -- )
  \item Can Kam (2024 -- )
  \item Chelsea Joe (2024 -- )
  \item Jacob Bacus (2024 -- )
  \item Rohan Goyal (2024 -- )
  \item Harrison Stropkay* (2024 -- )
  \item Abigayle McCusker (2024 -- )
  \item Torsha Chakraverty (2024 -- )
  \item Chloe Terestchenko (2024 -- )
  \item Ansh Motiani (2024 -- )
  \item Kaitlyn Peng* (2024 -- )
  \item Everett Tai (2024 -- )
  \item Andrew Cao (2024 -- )
  \item Michael Chen (2023 -- )
  \item Jake McDermid (2023 -- )
  \item Om Shah (2023 -- )
  \item Grady Redding (2023 -- )
  \item DJ Matusz (2023 -- )
  \item Sarah Parigela (2023 -- )
  \item Aaryan Agarwal (2023 -- )
  \item Maura Hough (2023 -- )
  \item Emma Reeder (2023 -- )
  \item Safwan Rashid (2023 )
  \item Francisca Fadairo (2023 -- )
  \item Ameer Talha Yasser (2023)
  \item Yue Zhuo (2023 -- )
  \item Megan Liu (2023 -- 2024)
  \item Charles Baker (2023)
  \item Andrew Shi (2023)
  \item Ash Chinta (2023)
  \item Xueyao Zheng (2023)
  \item Sergio Campos Legonia (2023)
  \item Jennifer Xu (2023 -- )
  \item Elias Emery (2023)
  \item Yvonne Chen (2023)
  \item William McCall (2023)
  \item Natalie Schreder (2023)
  \item Raselas Dessalegn (2023)
  \item Grace Wang (2023)
  \item Mira Chiruvolu (2023 -- 2024)
  \item Anna Mikhailova (2022)
  \item Ansh Patel (2022 -- )
  \item Ziyan Zhu (2022 -- )
  \item Benjamin Lehrburger (2022)
  \item Thomas Corrado (2022)
  \item Samuel Crombie (2022)
  \item Alexander Marcoux (2022)
  \item Jessna Brar (2022)
  \item Wenhua Liang (2022)
  \item Kevin Cao (2022)
  \item Goutham Veeramachaneni (2022)
  \item Zachary Somma (2022)
  \item Dawson Haddox (2022)
  \item Swestha Jain (2022)
  \item Aidan Adams (2021)
  \item Damini Kohli (2021)
  \item Kunal Jha* (2021 -- )
  \item Daniel Carstensen* (2021 -- )
  \item Brian Chiang (2021 -- 2022)
  \item Daniel Ha (2021)
  \item Darren Gu (2020 -- 2021)
  \item Tyler Chen (2020 -- 2022)
  \item Tehut Biru* (2020 -- 2021)
  \item Chris Suh (2020 -- 2021)
  \item Helen Liu (2020)
  \item Kelly Rutherford (2020)
  \item Chris Jun (2020 -- 2022)
  \item Ethan Adner (2020 -- 2022)
  \item Chris Long (2020 -- 2021)
  \item Esme Chen (2020 -- 2021)
  \item Luca Lit (2020)
  \item Vivian Tran (2020)
  \item Greg Han (2020)
  \item Austin Zhang (2020)
  \item Chelsea Uddenberg (2020)
  \item Shane Hewitt (2020)
  \item Chetan Palvuluri (2020)
  \item Aaron Lee (2019 -- 2020)
  \item Anne George (2019 -- 2020)
  \item Sarah Park (2019 -- 2020)
  \item Shane Park (2019 -- 2020)
  \item William Chen (2019 -- 2020)
  \item Tudor Muntianu (2019 -- 2021)
  \item William Baxley (2018 -- 2019)
  \item Ann Carpenter (2018)
  \item Seung Ju Lee (2018)
  \item Mustafa Nasir-Moin (2018)
  \item Iain Sheerin (2018)
  \item Darya Romanova (2018)
  \item Alejandro Martinez (2018 -- 2020)
  \item Rachael Chacko (2018)
  \item Kirsten Soh (2018)
  \item Paxton Fitzpatrick* (2017 -- 2019)
  \item Stephen Satterthwaite (2017 -- 2018)
  \item Bryan Bollinger (2017 -- 2018)
  \item Christina Lu (2017)
  \item Armando Oritz (2017)
  \item Campbell Field (2016 -- 2018)
  \item Madeline Lee (2016 -- 2020)
  \item Wei Liang Samuel Ching (2016 -- 2017)
  \item Marisol Tracy (2016 -- 2017)
  \item Allison Frantz (2016 -- 2017)
  \item Aamuktha Porika (2016 -- 2017)
  \item Jake Rost (2016)
  \item Clara Silvanic (2016)
  \item Aman Agarwal (2016)
  \item Joseph Finkelstein (2016)
  \item Sheherzad Mohydin (2016)
  \item Peter Tran (2016)
  \item Gal Perlman (2016)
  \item Jessica Tin (2016)
\end{etaremune}
\end{multicols}

% \subsubsection*{Princeton University}
% \years{2012--2015} \textit{Co-supervisor}:\\
% Jeremy Cohen (undergraduate)\\
% Luis Piloto (research assistant; now: Google DeepMind)\\
% Kimberly L. Stachenfeld (doctoral student; now: Google DeepMind)\\
% Jamal Williams (research assistant; now: graduate student, Princeton University)\\[0.05cm]

% \years{2013--2014} \textit{Organizer}, Machine Learning Reading Group

% \subsubsection*{University of Pennsylvania}
% \years{2009--2011} \textit{Co-supervisor}:\\
% Gaurav Bharaj (masters student)\\
% Timothy Lew (undergraduate; now: graduate student, UCSD)\\
% Ningcheng Li (masters student; now: Yale Medical School)\\
% Andrew Spelman (undergraduate)

% \years{2011}  \textit{Instructor}, Computational Neuroscience (Summer course)\\
% \years{2010}  \textit{Instructor}, Computational Neuroscience (Summer
% course)\\
% \textit{Guest lecturer}, Human Memory (topic: Hopfield networks)\\
% \years{2009}  \textit{Co-instructor, Teaching assistant}, Computational Neuroscience (Summer course)\\
% \years{2008}  \textit{Teaching assistant}, Introduction to Brain and
% Behavior

% \subsection*{Brandeis University}
% \years{2005--2006}  \textit{Computer Science Undergraduate Department
%   Representative}\\
% \years{2005}
% \textit{General teaching assistant}, Programming in Java and C; Structure and Interpretation of Computer Programs; Internet and Society

\section*{Service}
\subsection*{Professional organizations}
\begin{etaremune}
\item Dartmouth-Kalaniyot (2024 -- ) Co-founder, Board member

\item National Science Foundation (2023, 2024, 2025) Panel member

\item NeuroMatch Academy (2021 -- ) Developer and project mentor (computational neuroscience and deep learning tracks)

\item Artificial Intelligence and Statistics (AISTATS; 2021 -- 2024) Area
chair (natural language processing and machine learning)

\item Methods in Neuroscience at Dartmouth (MIND) Summer School (2017 -- ) Co-founder
\end{etaremune}


\subsection*{Dartmouth committee memberships}
\begin{etaremune}
\item Social (Department Well-Being) Committee (2023--2024, 2024--2025)
\item Undergraduate Committee (2021--2022, 2015--2016)
\item Graduate Committee (2020--2021, 2016--2019)
\item Cognitive Neuroscience Faculty Search Committee (2018)
\item Molecular and Systems Biology Faculty Search Committee (2017)
\item Cognitive Neuroscience Faculty Search Committee (2016)
\end{etaremune}

\subsection*{Ad-hoc reviewer}
\textit{Advances in Cognitive Psychology},
\textit{Agence Nationale de la Recherche},
\textit{American Journal of Psychology},
\textit{Cell Reports},
\textit{Cerebral Cortex},
\textit{Cognition},
\textit{Cognition and Emotion},
\textit{Cortex},
\textit{Computational and Systems Neuroscience (Cosyne)},
\textit{eLife},
\textit{International Conference on Machine Learning (ICML)},
\textit{International Joint Conference on Artificial Intelligence},
\textit{International Journal of Social Research Methodology},
\textit{Israel Science Foundation},
\textit{Journal of Cognitive Psychology},
\textit{Journal of Mathematical Psychology},
\textit{National Science Foundation (USA)},
\textit{Nature},
\textit{Nature Communications},
\textit{Nature Computational Science},
\textit{Nature Human Behaviour},
\textit{Neural Computation},
\textit{NeuroImage},
\textit{Neural Information Processing Systems (NeurIPS)},
\textit{Neuropsychologia},
\textit{PLoS Biology},
\textit{PLoS Computational Biology},
\textit{Proceedings of the National Academy of Sciences},
\textit{Psychological Reports},
\textit{Psychological Review},
\textit{Psychonomic Bulletin and Review},
\textit{Science},
\textit{Scientific Data},
\textit{Scientific Reports},
\textit{Society for Artificial Intelligence and Statistics (AISTATS)},
\textit{Swiss National Science Foundation},
\textit{The Journal of Neuroscience}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

\begin{center}
{\scriptsize Last updated: \today} % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
% Local Variables:
% TeX-engine: xetex

% End:
